---
title: "`r params$title`"
author: "Ryan Heslin"
date: "`r format(Sys.Date(), '%B %e, %Y')`"
header-includes:
  - \setlength{\parindent}{2em}
  - \setlength{\parskip}{2em}
params:
    title: "Classifying Campaign Images with a Convolutional Neural Network: Initial Report"
output:
  pdf_document:
    highlight: "kate"
    df_print: "kable"
url_color: "blue"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = "",
  fig.pos = "",
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  highlight = TRUE
)

```


```{r, child = here::here("R/eda/classifier.Rmd")}
```

At present, I see the following areas to improve: 
\begin{enumerate}
\item Separating images of text logos from images of candidates. RESNET18, and CNNs 
generally, are not suited for text recognition, so these training examples are not useful to the model. 
Separating the two types of images by hand would be tedious but doable, but there may be a programmatic way of.
doing so
\item  Customizing the neural network I currently am using RESNET18 almost unmodified. I could try 
including more weights in gradient computations, or designing my own network with a different (probably simpler).
architecture
\item Hyperparameter customization. From my limited knowledge, tuning learning rate, batch size, and other. 
hyperparameters is largely guesswork, but necessary to produce useful models.
\item Experimenting with preprocessing. Cropping, flipping, etc., could be used to generate more training examples. `torchvision` has functions for many different transformations.
\end{enumerate}

